### 2013-07-24 doc/asplos14/conclude.tex
back to space limit

Depending on the benchmark, \Grappa is between 11X faster and 5.4X
slower than MPI and UPC, and between 2.6X faster and 4.3X slower than
the XMT. When \Grappa is slower than MPI, we find that the MPI
implementation includes a specialized implementation of a feature
\Grappa provides generally to all applications. This generality comes
at a performance cost but eases the application developer's
task. Moreover, significant tuning has yet to be done on the \Grappa
runtime system.  Yet when cost-performance is considered, mass-market
x86-based cluster hardware makes \Grappa a highly attractive option.

>>>>

Depending on the benchmark, \Grappa is between 11X faster and 5.4X
slower than MPI and UPC, and between 2.6X faster and 4.3X slower than
the XMT. When \Grappa is slower than MPI, we find that the MPI
implementation includes a specialized implementation of a feature
\Grappa provides generally to all applications. This generality comes
at a performance cost but eases the application developer's
task. Moreover, there are significant tuning opportunities the \Grappa
runtime system.  When cost-performance is considered, \Grappa on mass-market
x86-based clusters is a highly attractive option.

### 2013-07-24 doc/asplos14/evaluation.tex
fixed figure rotation
back to space limit

\begin{table*}[htb]
\begin{center}
\begin{tabular}{l|c|c|c|c|c}
% remember: bfs time is mean_time * nbfs
                               &   GUPS            &   BFS   & IntSort & UTS & Pagerank \\ \hline
Application message rate/core  & 984K/s            &  983K   &           \\
%Application message bytes     & 31.8 $\pm$ 1.2    & \\
Avg. Application message bytes & 31.8              & 33.9    &       \\
Network bandwidth per node     & 478MB/s           & 511MB/s &          \\
%Network message bytes         & 23.2K $\pm$ 12.4K & \\ \hline
Avg. Network message bytes     & 23.2K             & 4.3K    &     \\ \hline
Avg. active tasks/core         & 0.9               & 58.2    &    \\
Max. active tasks/core         & 1                 & 128     &     \\
Avg. ready queue length/core   & 2.3               & 6.1     &      \\
Avg. Context switch rate/core & 34.2K/s           & 539K/s  &       \\ 
Steal count                    & 0                 & 0       &       \\
\end{tabular}
\end{center}
\caption{Internal runtime metrics, for 64-node, 16-core-per-node benchmark runs}
\label{tab:grappa-metrics}
\end{table*}

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[height=0.5\textwidth]{results/plot_concurrency.pdf}
    \end{center}
    \caption{Throughput, request latency, and idleness as number of concurrent workers is varied}
    \label{fig:grappa-concurrency}
\end{figure}

>>>>

\begin{table}[htb]
\small
\begin{center}
\setlength{\tabcolsep}{1pt}
\begin{tabular}{l|c|c|c|c|c}
% remember: bfs time is mean_time * nbfs
                               &   GUPS            &   BFS   & IntSort & UTS & Pagerank \\ \hline
App. message rate/core (K/s)  & 984            &  983   &      &     \\
%Application message bytes     & 31.8 $\pm$ 1.2    & \\
Avg. App. message bytes & 31.8              & 33.9    &      & \\
Network BW per node (MB/s)    & 478           & 511 &    &      \\
%Network message bytes         & 23.2K $\pm$ 12.4K & \\ \hline
Avg. Network message bytes     & 23.2K             & 4.3K    & &    \\ \hline
Avg. active tasks/core         & 0.9               & 58.2    &  &  \\
Max. active tasks/core         & 1                 & 128     &  &   \\
Avg. ready queue length/core   & 2.3               & 6.1     &  &    \\
Avg. Ctx switch rate/core (K/s) & 34.2           & 539  &     &  \\ 
Steal count                    & 0                 & 0       &  &     \\
\end{tabular}
\end{center}
\caption{Internal runtime metrics, for 64-node, 16-core-per-node benchmark runs}
\label{tab:grappa-metrics}
\end{table}

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[height=0.5\textwidth, angle=90]{results/plot_concurrency.pdf}
    \end{center}
    \vspace*{-0.25in}
    \caption{Throughput, request latency, and idleness as number of concurrent workers is varied}
    \label{fig:grappa-concurrency}
\end{figure}
